### 2023-10-09 main.tex
fixx
fix 1

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}

@@

\textbf{Remark}: In case of $N=2$ we can argue as in the case of $|\Psi^{''}\rangle$ and we obtain 
	|\Psi^{'}\rangle= 

@@

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\mathbbm{1}_{\{c_{1}+\ldots+c_{L}>0\}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\\&\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}

@@

\textbf{Remark}: If we stop distinguishing the types of particles we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}. Indeed, introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes

>>>>

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{x=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{y}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}

@@

\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. 

@@

%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}. If we stop distinguishing types of non-empty particles we have that \eqref{ABS} reads
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)\dt
where $x_{k}$ denotes the position of the particle $k$ among $q$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}\dt
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-\ell_{k}-(q-k+1)\right)\dt
\begin{equation}\label{PsiI-N2}
\Psi^{'}(\bm{\ell},q)=\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-\ell_{k}-q+k\right)}{(2+L-k)}\dt
where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. 

@@

\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}. Indeed, by adapting \eqref{PsiI-N2} we obtain 
\begin{comment} introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
